---
title: "R Notebook"
output:
  html_document: default
  html_notebook: default
---

## Tibbles

```{r}
library(readxl)
library(dplyr)
library(plyr)
library(tricky)
#download.file(
#  url = "http://www.data.gouv.fr/fr/datasets/panorama-des-grands-projets-si-de-letat-1/", 
#  destfile = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx"
#  )

read_excel(path = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx") %>%   glimpse()
```

### Standardize variable names

- `str_standardize()` takes a table and return standardized variable names (ie remove blank spaces and replace them with "_")
- `set_standard_names()`takes a table and return a table with standardized variable names

```{r}
read_excel(
  path = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx"
  ) %>% 
  setNames(str_standardize(.)) %>%
  glimpse()
```


```{r}
read_excel(
  path = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx"
  ) %>% 
  set_standard_names() %>%
  glimpse()
```

### Missing values

* `count_na()` returns a table of missing and non-missing values in a vector
* `detect_na()` returns a table with the number and the share of missing values for each variable

```{r}
read_excel(path = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx") %>% 
  set_standard_names() %>% 
  .$ministere_porteur %>% 
  count_na()
```

```{r}
read_excel(path = "raw-data/DINSIC-Panorama_des_grands_projets_SI_20161116.xlsx") %>% 
  set_standard_names() %>% 
  detect_na()
```
