---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r}
library(tricky)
library(tibble)
```

Suppose we have a dataset with for each row the name of a node and the name of a group it belongs to. We want to have a dataset with all relationships between nodes (ie if A and B belong to the group a, they have one relationship.)

* `make_single_node_node_table_` makes a table with one row for each relationship for a single node. 
* `make_node_node_table_` makes a table with one row for each relationship for all nodes

```{r}
toy_data <- tibble::tibble(
  node = c("A", "B", "C", "A", "B"),
  link = c("a", "a", "b", "b", "b")
  )
toy_data
```

```{r}
make_single_node_node_table_(
  .data = toy_data,
  .id = "A", 
  node = "node",
  link = "link"
  )
```

```{r}
make_node_node_table_(
  .data = toy_data,
  node = "node",
  link = "link"
  )
```

