---
title: "Tibbles"
author: "Paul-Antoine Chevalier"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, message=FALSE}
library(readxl)
library(dplyr)
library(plyr)
library(tricky)
library(tibble)
library(readr)
library(knitr)
```

## Find keys

* `find_keys()` looks at a table and returns a data frame with the name of all available keys.

```{r findkeys}
read_csv(
  system.file(
    "extdata", 
    "table_deputes.csv", 
    package = "tricky")
  ) %>% 
  find_keys() 
```

## Standardize table names

Many datasets have non standard variable names including accents (ie é, è, à, ...), spaces and so on. 

The French IT Dashboard is an example of a data set with column names in natural language : 

```{r itdashboard-names}
read_excel(
  path = system.file(
    "extdata", 
    "panorama.xlsx", 
    package = "tricky"
    )
  ) %>% 
  names()
```

* `set_standard_names` takes a table and returns the same table with standardized names

```{r str-standardize}
read_excel(
  path = system.file(
    "extdata", 
    "panorama.xlsx", 
    package = "tricky"
    )
  ) %>% 
  set_standard_names() %>% 
  glimpse()
```

## Detect missing values

* `count_na()` returns a table of missing and non-missing values in a vector
* `detect_na()` returns a table with the number and the share of missing values for each variable

```{r count-na}
read_excel(
  path = system.file(
    "extdata", 
    "panorama.xlsx", 
    package = "tricky"
    )
  ) %>% 
  set_standard_names() %>% 
  .$ministere_porteur %>% 
  count_na()
```


```{r detect-na}
read_excel(
  path = system.file(
    "extdata", 
    "panorama.xlsx", 
    package = "tricky"
    )
  ) %>% 
  set_standard_names() %>% 
  detect_na()
```
